### 2024-10-24 manuscript.tex
Minor edits

In general, sea surface temperature (SST) biases in the SO can originate either
in the atmosphere, caused by too much shortwave heating of the surface, too
little longwave cooling of the surface, or in the ocean circulation.
Interactions of both are also possible, due to, for example SST affecting
clouds and clouds affecting the surface radiation.  \cite{zhang2023} have shown
that SST biases have improved in CMIP6 compared to CMIP5 (relative to ERA5),
with SST overall increasing in the later CMIP phase. However, over the SO this
resulted in an even higher positive bias, especially in the Atlantic Ocean (AO)
sector of the SO, increasing by up to 1°C.  \cite{luo2023} identified that the
SO SST bias in an ensemble of 18 CMIP6 models originates not from the surface
heat and radiation fluxes (using reanalyses as a reference), but from a warm
bias in the Northern Atlantic Deep Water.

@@

Altogether, we analysed about 2400 days of data from 31 voyages, and one
sub-Antarctic station covering diverse longitudes and latitudes of the SO. To
achieve a like-for-like comparison with the model, we used a ground-based lidar
simulator called the Automatic Lidar and Ceilometer Framework [ALCF;
\cite{kuma2021}]. We contrasted the results with the European Centre for
Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 [ERA5; \cite{era5}] and the
Modern-Era Retrospective analysis for Research and Applications, Version 2
[MERRA-2; \cite{gelaro2017}].

@@

ERA5 \citep{era5} is a reanalysis produced by the European Centre for
Medium-Range Weather Forecasts (ECMWF). It is based on a numerical weather
prediction model IFS version CY41R2.  The horizontal resolution is 0.25° in
latitude and longitude, which is about 28 km in the North--South direction and
14 km in the East--West direction at 60°S.  Internally, the model uses 137
vertical levels. Here, we use output at 1-hourly instantaeous time intervals,
except for radiation quantities, which are accumulations (from these we
calculate daily means).  Vertically resolved quantities are made available on
37 pressure levels.

>>>>

In general, sea surface temperature (SST) biases in the SO can originate either
in the atmosphere, caused by too much shortwave heating of the surface, too
little longwave cooling of the surface, or in the ocean circulation.
Interactions of both are also possible, due to, for example SST affecting
clouds and clouds affecting the surface radiation.  \cite{zhang2023} have shown
that SST biases have improved in CMIP6 compared to CMIP5 [relative to the
European Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5; ERA5],
with SST overall increasing in the later CMIP phase. However, over the SO this
resulted in an even higher positive bias, especially in the Atlantic Ocean (AO)
sector of the SO, increasing by up to 1°C.  \cite{luo2023} identified that the
SO SST bias in an ensemble of 18 CMIP6 models originates not from the surface
heat and radiation fluxes (using reanalyses as a reference), but from a warm
bias in the Northern Atlantic Deep Water.

@@

Altogether, we analysed about 2400 days of data from 31 voyages, and one
sub-Antarctic station covering diverse longitudes and latitudes of the SO. To
achieve a like-for-like comparison with the model, we used a ground-based lidar
simulator called the Automatic Lidar and Ceilometer Framework [ALCF;
\cite{kuma2021}]. We contrasted the results with ERA5 \citep{era5} and the
Modern-Era Retrospective analysis for Research and Applications, Version 2
[MERRA-2; \cite{gelaro2017}].

@@

ERA5 \citep{era5} is a reanalysis produced by the ECMWF.  It is based on a
numerical weather prediction model IFS version CY41R2.  The horizontal
resolution is 0.25° in latitude and longitude, which is about 28 km in the
North--South direction and 14 km in the East--West direction at 60°S.
Internally, the model uses 137 vertical levels. Here, we use output at 1-hourly
instantaeous time intervals, except for radiation quantities, which are
accumulations (from these we calculate daily means).  Vertically resolved
quantities are made available on 37 pressure levels.
